Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-05-20 review/response-letter.tex

Dear Referees, Dr. Kurniawati:

\vspace{1em}

We greatly appreciate your time and effort in providing us with an invaluable assessment of our work, helping us to significantly improve both the quality and presentation of our energy-aware planning-scheduling for the aerial robotics domain. We have been able to address all your comments and questions in a revised version that we have attached once again for your kind consideration.

The response letter is split into three sections, the first two for each review and the third for the editor's report. The referees' comments are in black, and our response is highlighted in blue, similarly to the edits in the attached revised version. The quotes from the revised version are incorporated here in a box with a light red background and a thick red left border.

@@

{\color{blue}

{\hspace*{-4.5em}{[R1]}\vspace*{-1.9em}}

We would like to thank the first referee for assessing our work with great detail, proposing edits, and posing important questions. These helped us to strengthen our contribution and clarify aspects we did not consider in the first version.

%In this work, we choose to leverage planning-scheduling to aerial robotics, as we believe this is a relevant application and advantageous system for our devised approach. We are thus excited to see the referee sharing similar findings while bringing up numerous important points.
}

@@

2. Line 24-27 of algorithm 2 only re-plans $c_i^\rho$. What about $c_i^\sigma$? Since the re-planning is conducted after solving the MPC, optimality can not be claimed for the re-planning. It's possible that there are multiple options to adjust the parameters during re-planning: 1. simultaneously adjusting both $c_i^\rho$ and $c_i^\sigma$; 2. only adjust $c_i^\rho$; 3. only adjust $c_i^\sigma$. It might be useful to consider all of these cases and discuss how they affect optimality.

{\color{blue}

{\hspace*{-4.5em}{[R1:2]}\vspace*{-1.9em}}

Thank you for the comment as well as for proposing a way to address the issue. We do not use the model predictive controller (MPC) to plan both the parameters due to the practical feasibility of re-planning in flight and the different effects of the computation and path parameters on the energy consumption. The computation parameters have an immediate effect, i.e., they affect instantaneous energy consumption, whereas the path parameters affect the flight time, i.e., they affect the overall energy consumption. 
Concretely and by assumption, a change in the computations alters the schedule, and therefore the drained power by the computing hardware on the aerial robot, whereas a change in the path parameters alters the time when the aerial robot terminates the coverage.

We have thus decided to utilize a hybrid approach. We employ MPC for the schedule (computation parameters $c_i^\sigma$) in Line 16 and a heuristics-based greedy approach for the coverage (path parameters $c_i^\rho$) in Lines 24–27.
A similar combination of techniques has been investigated in the past planning-scheduling literature by Ondr\'{u}\v{s}ka et al.~(reference [{\color{green}17}] in the revised manuscript).

We have updated the algorithm in Line 16, reflecting the observation as this was not in the original manuscript.

@@

\begin{formal}
\begin{algorithmic}[1]
  \small
    \makeatletter
    \setcounter{ALC@line}{15}
    \makeatother
    \color{blue}\STATE $\mathbf{q}(\mathcal{K}\setminus\{t+N\}),c_i^\sigma(\mathcal{K})\gets${ \vspace*{.3ex}solve NLP }$\argmax_{\mathbf{q}(k),c_i(k)}$\newline \vspace*{.7ex}\hspace*{1em}${l_f(\mathbf{q}(t+\hspace*{-.1ex}N),t+\hspace*{-.1ex}N)}+\hspace*{-.2ex}{\sum_{k\in\mathcal{K}}{l_d(\mathbf{q}(k),c_i(k),k)}}${ in Eq.~({\color{red}18})\newline \hspace*{1em}on }$\mathcal{K}=\{t,t+h,\dots,t+N\}$\vspace*{.3ex}

    \vspace*{.8ex}
  \end{algorithmic}
\end{formal}

  We have updated the introduction and the problem formulation in Section II to address the observation, and further added an explanatory text in Section IV.B as well as in the conclusion. In the introduction we have stated explicitly that we utilize both the heuristics and optimal control.

@@

  \begin{formal}
  {\color{black} [...] our approach uses optimal control {\color{blue} and heuristics} where both the paths and schedules variations are trajectories, varying between given bounds [...]} Hybrid approaches~[{\color{green}17}] are also available, where the techniques are mixed.
  \vspace*{1ex}
  \end{formal}

  We have updated the problem formulation, clearly stating that the objective is to find energy-aware trajectory of parameters rather than optimal.

@@

{\color{blue}

{\hspace*{-4.5em}{[R1:4]}\vspace*{-1.9em}}

Thank you for the concern regarding the readability of the figure. We have split the figure into two figures, 6 and 7. Sub-figures that are related are then on a separate row, each for one case. I,II in Figure 6 are related to CPP at boundary values of path parameters and varying atmospheric conditions, and i,ii Figure 7 are related to planning-scheduling of I,II with varying battery conditions. We have rewritten the captions, adding additional commentary to ease the understanding.

\begin{formal}
  \footnotesize
  \input{../figures/results/new_physics2/new_trajs-ener_I-II.tikz}
  {\color{blue}Fig.~6:~\color{blue}CPP with Zamboni-like motion using two boundary configurations. In {\color{red}a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}. In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions. In {\color{red}c} are the states of the energy model for {\color{red}I}.
  \vspace*{1ex}
  }
\end{formal}
\begin{formal}
  \footnotesize
  \input{../figures/results/new_physics2/new_trajs-ener_LOWER_i-ii.tikz}
  \vspace*{-.6ex}
  {\color{blue}
  Fig.~7:~Planning-scheduling of CPP and ground patterns detections% with PedNet CNN
  , utilizing the lowest configuration {\color{red}I} as a starting point in {\color{red}i} and the highest {\color{red}II} in {\color{red}ii} while varying atmospheric (same as Fig.~{\color{red}6}) and battery conditions. In {\color{red}a} are the re-planned trajectories, in {\color{red}b} the parameters, and in {\color{red}c} the energy w.r.t. the battery.}
  \vspace*{1ex}
\end{formal}
}

@@

6. The following paper is related to this letter and the authors could consider referencing it.
\begin{itemize}
  \item Di Franco, Carmelo, and Giorgio Buttazzo. ``Coverage path planning for UAVs photogrammetry with energy and resolution constraints.'' Journal of Intelligent Robotic Systems 83, no. 3 (2016): 445-462.
\end{itemize}

{\color{blue}

{\hspace*{-4.5em}{[R1:6]}\vspace*{-1.9em}}

Thank you for bringing Di Franco and Buttazzo's past work to our attention. We have considered another past study by the authors ``Energy-aware coverage path planning of UAVs'' from 2015, and the proposed work appears to be an extension. %Both studies do not account for the energy contribution of the computations but interestingly propose the variability of the cover by changing the distance of the survey lines in the boustrophedon motion. Whilst similar to our Zamboni-like motion, the cover variability is not achieved in flight nor applies to constrained aerial robots such as fixed wings--which we consider due to a narrower computation-motion energy difference--but rather rotary wings.

@@

4. In Definition II.1, the use of $\mathbf{p}(t)$ is confusing. I assume $\mathbf{p}$ is an arbitrary point on the path, but $\mathbf{p}(t)$ usually refers to a trajectory.

{\color{blue}

{\hspace*{-4.5em}{[R1:10]}\vspace*{-1.9em}}

Thank you for underlying the issue. We have not realized this possible source of additional confusion and decided to utilize only $\mathbf{p}$ to designate a point. We have updated the occurrence in the remainder of the work, for consistency. Apart from Definition II.1 that we showed in point 7, the occurrence was in the definition of path functions.

@@

6. Could you please explain how you obtain matrix $A$ and $C$ in (6) and (7), or put some reference?

{\color{blue}

{\hspace*{-4.5em}{[R1:12]}\vspace*{-1.9em}}

Thank you for noticing that a citation and clarification are missing regarding the energy models. The items of matrices $A$ and $C$ are constructed so that the two periodic models, the model in Equation ({\color{red}2}) and Equation ({\color{red}3}) match under some conditions (the value of the initial guess is described by Equation ({\color{red}8}) and the model is not perturbed by the control).

$A$ is then a skew-symmetric matrix that contains sub-matrices $A_j$ utilized for the periodic behavior with the frequencies $\omega:=2\pi/T$ ($T$ is the period). Each frequency is multiplied by $j$ from one up to the order $r$, where $j$ is the index of the sub-matrix, i.e., there are $r$ frequencies modeling the periodicity one the base frequency.

@@

The contributions of this paper are 1) an energy model that predicts the impact of the effect of changes to the path or computation energy on the battery in the future 2) introduction of Zamboni-like motion patterns that can be replanned while on the path itself 3) an optimal control problem and solution to solve the re-planning coverage problem to decide how to change the computations and the path to optimize the energy usage

{\color{blue}

{\hspace*{-4.5em}{[R2]}\vspace*{-1.9em}}

We would like to thank the second referee, especially for the summary of our work and the kind commentary on the relevance and difficulty of accounting for both motion and computations energies in planning for aerial robots. %Indeed, we believe that planning-scheduling as a sub-topic of motion planning is still very nascent for aerial robots and hope that this work continues to build upon previous successes in planning-scheduling for mobile robots. We are thus excited to comment on and alter the manuscript as necessary, as the second referee brings up a lot of great points.

@@

- Not made clear how this is different from other relevant works such as work cited ``C. Di Franco and G. Buttazzo, ``Energy-aware coverage path planning of UAVs,'' in Int. Conf. on Autonomous Robot Syst. and Competitions. IEEE, 2015, pp. 111–117''; especially when stating ``These studies are focused on ground-based robots [9], [19], [23], [24], yet, aerial robots are particularly affected by energy considerations, as it would be generally required to land to recharge the battery''; since this is not the first with aerial robots, what about this research is different from other work on energy aware CPP? Summarize clearly differences in related work in UAV literature.

{\color{blue}

{\hspace*{-4.5em}{[R2:1]}\vspace*{-1.9em}}

Thank you for bringing Di Franco and Buttazzo's past study to our attention. We have considered the work in the original manuscript in terms of the coverage algorithm in Section IV-A, utilizing it as a reference for aerial coverage. We have not included it in the introductory material as the work does not account for the energy expenditure of computations, nonetheless, we agree on the necessity to clarify this in the introduction. To this end, we have added explanatory text in the introduction that--aside the proposed work--includes the follow-up work by the same set of authors proposed by the first referee.

@@

- High-level comment: the paper would benefit from restructuring for clarity to better convey the interesting technical ideas. At present, difficult to understand the insights behind the main contributions. For example, ``the re-planning-scheduling problem is finding the optimal trajectory of parameters $c_i$ in time.'' -- optimal w.r.t. what objective function? Total energy? Mission duration? Make this clear in the problem definition section.

{\color{blue}

{\hspace*{-4.5em}{[R2:2]}\vspace*{-1.9em}}

Thank you for the high-level comment and for proposing to state clearly the objective function. Regarding the objective function, we have integrated the problem definition accordingly, whereas we have improved the text in the manuscript by both implementing the specific comments and rewriting some technical details or adding further commentary.

@@

  Also, ``The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds [12] and frequency and voltage of the computing hardware [9], [13], [14]. We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage'' --$>$ What are the actual computation inputs that can be changed? It is unclear throughout the paper what $c_i^\sigma$ is.

  {\color{blue}

  {\hspace*{-4.5em}{[R2:3]}\vspace*{-1.9em}}

  Thank you for underlying the need to state clearly what the computations parameters refer to. We have not realized this point was not stated explicitly earlier than in the experimental setup. Our purpose is to alter the granularity (specific examples are provided below) at which different computations run so that the energy consumption required by the computing hardware onboard the aerial robot increases or decreases.

@@

  In addition, what is the performance metric we want to observe improving using the algorithm 2 in the numerical experiments (comparing i, ii to I, II baselines)?

  {\color{blue}

  {\hspace*{-4.5em}{[R2:4]}\vspace*{-1.9em}}

  Thank you for noticing the comparison was missing in the manuscript. We utilize as a performance metric the weighted average configuration of parameters divided by the battery state of charge at the end of the flight, meaning the higher the average value of parameters and the lowest the battery state of charge the better (all the resources are being utilized). We have added explanatory text to the simulation results to report the metric for i and ii against I and II respectively.

  \begin{formal}\color{black}[...] 
    {\color{blue}
Assuming both the parameters are weighted equally, and the initial battery SoC is seventy percent, {\color{red}I} would not be able to complete the flight, and {\color{red}II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
Nonetheless, performance metrics of {\color{red}i} and {\color{red}ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx. 45 and 35 percent for {\color{red}i}, and 62 and 87 percent for {\color{red}ii}.}  
    \vspace*{1ex}
  \end{formal}
  }

@@

{\color{blue}

{\hspace*{-4.5em}{[R2:5]}\vspace*{-1.9em}}

Thank you for suggesting adding a clear indication of what performance metric is being utilized. Indeed this information was missing in the original manuscript. We have added explanatory text in Problem Formulation to address the point.

\begin{formal}\color{black}

  The problem %of planning-scheduling 
  is {\color{blue}split into }%composed of 
  %two%sub-problems.
  {\color{blue}the derivation }%. One is 
  %to form a %static 
  {\color{blue} of} a {\color{blue}coverage} plan %that visits every point in space 
  {\color{blue}and its} {\color{blue}energy-aware} %other to
  re-plan{\color{blue}ing} and -schedul{\color{blue}ing } %the plan 
  in-flight. %in an energy-aware way. %{\color{blue}, whereas }
  {\color{blue} 
  The re-planning-scheduling improves a performance metric, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
  the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent. The objective is then high average parameters configuration and battery usage.
  %The performance metric the re-planning-scheduling %in the letter 
  %improves is %then
  %the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
  %SoC.% at the end of the flight.
  }
\vspace*{1ex}
\end{formal}
}

@@

  Average results from more numeric experiments (e.g., average flights competed on baseline vs. with new algorithm) would also really benefit the paper. Paper would also be greatly strengthened by actual physical experiments on UAV.

  {\color{blue}

  {\hspace*{-4.5em}{[R2:6]}\vspace*{-1.9em}}

  Thank you for this point; we have reduced the number of experimental results due to space constraints. Nonetheless, we agree that additional results would further justify the need for planning-scheduling in the aerial robotics domain. To this end, we have added the average result for eight flights derived utilizing the flight simulation capabilities of the open-source Paparazzi flight control software for autonomous aerial vehicles. These results are derived in two equally sized sets, each similar to flights i and ii in the manuscript. The results are described thoroughly in the corresponding author's Ph.D. thesis (reference [{\color{green}31}], Section 6.3.2).

  We have updated the numerical simulation section accordingly.

@@

- Figure 1 not clear; are we supposed to be able to differentiate between i, ii, and iii paths? Not able to differentiate currently, so unable to understand key takeaway of figure. What is the meaning of the colors (green for i, red for ii/iii)?

{\color{blue}

{\hspace*{-4.5em}{[R2:9]}\vspace*{-1.9em}}

Thank you for noticing the issue regarding poor clarity. We have updated the figure and added a legend to clarify the meaning of i, ii, and iii as different stages in planning-scheduling.

@@

Overall, the paper addresses a very interesting topic and brings together many different techniques to solve a challenging problem. It could be strengthened with more attention to clarity to convey the technical insights and more experiments showing an improvement in a performance metric of interest.

{\color{blue}

{\hspace*{-4.5em}{[R2:12]}\vspace*{-1.9em}}

Thank you once again for the commentary as well as for bringing up a lot of important points. We are indeed excited about the potential of planning-scheduling for the aerial robotics domain to address autonomy and other criticalities arising in a number of use cases. 
We hope our updates according to the suggestions and comments have helped to improve the technical insights of our work.
%We would like to propose a revised version of the manuscript for your kind consideration, where we incorporate the points and additional experimental results.}
}

@@

\vspace{1em}

\vspace{2em}

{Associate Editor}

{\hspace*{-4.5em}\textbf{[AE]}\vspace*{-1.9em}}

This paper received two quality reviews. Both reviewers have a favorable impression of the work with specific suggestions for improvement. The authors should take care to address the concerns of the reviewers in a revised version. Both reviewers specifically mention a related work that should be cited, as well as specific concerns to improve the clarity of the technical contribution of the work.

{\hspace*{-4.5em}{[AE]}\vspace*{-1.9em}}

We thank the editor for handling our manuscript on planning-scheduling for the aerial robotics domain and the summary of the main concerns from the two reviews. 
We have incorporated all of the points proposed to strengthen and improve our contribution, making numerous modifications to the manuscript. Regarding the related work, we have updated the manuscript to include detailed commentary on how our approach differs.

We thus believe that with these edits, we have significantly improved the clarity of the technical contribution of our work and are excited to bring the revision version for your kind consideration.
}

### 2022-05-20 energy-planning.tex
updated w/ Hector's comments

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
  \thanks{The work was partly funded by EU grant No. 779882 (TeamPlay). The work for H. G. is supported by the Ramon y Cajal grant No. RYC2020-030090-I.}
  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
  \thanks{$^{\text{1}}$A. S. is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS. Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
  \thanks{$^{\text{2}}$H. G. is with the Department of Computer Architecture and Technology, University of Granada, Spain;} 
  \thanks{$^{\text{3}}$H. S. M.,  U. P. S. are with the SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
  University of Southern Denmark.}
  \thanks{Digital Object Identifier (DOI): see top of this page.}
}

@@

The problem %of planning-scheduling 
is {\color{blue}split into }%composed of 
two%sub-problems.
{\color{blue}: }%. One is 
to form a %static 
plan that visits every point in space {\color{blue}and }%the other to
re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
{\color{blue} 
The re-planning-scheduling improves the performance metric of quality of the plan and schedule against battery state of charge (SoC), i.e., the weighted average value of parameters divided by the remaining SoC.
%The performance metric the re-planning-scheduling %in the letter 
%improves is %then
%the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
%SoC.% at the end of the flight.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery at future time instants. To this end, Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies as well as battery evolution.

>>>>

%% author names and affiliations
\author{
  Adam Seewald$^{\text{1}}$, H\'ector Garc\'ia de Marina$^{\text{2}}$, Henrik Skov Midtiby$^{\text{3}}$, and Ulrik Pagh Schultz$^{\text{3}}$
  \thanks{The work was partly funded by EU grant No. 779882 (TeamPlay). The work for H. G. is supported by the Ramon y Cajal grant No. RYC2020-030090-I.}
  \thanks{Manuscript received: Month, Day, Year; Revised Month, Day, Year; Accepted Month, Day, Year.}%Use only for final RAL version
  \thanks{This paper was recommended for publication by Editor Editor A. Name upon evaluation of the Associate Editor and Reviewers' comments.} %Use only for final RAL version
  \thanks{$^{\text{1}}$A. S. is with the Department of Mechanical Engineering and Material Science, Yale University, CT, USA, but the work was performed while affiliated with the SDU UAS. Email: {\tt\footnotesize \href{mailto:adam.seewald@yale.edu}{adam.seewald@yale.edu}};}
  \thanks{$^{\text{2}}$H. G. is with the Department of Computer Architecture and Technology and with CITIC, University of Granada, Spain;} 
  \thanks{$^{\text{3}}$H. S. M.,  U. P. S. are with the SDU UAS, %M{\ae}rsk Mc-Kinney M{\o}ller Institute, 
  University of Southern Denmark.}
  \thanks{Digital Object Identifier (DOI): see top of this page.}
}

@@

The problem %of planning-scheduling 
is {\color{blue}split into }%composed of 
%two%sub-problems.
{\color{blue}the derivation }%. One is 
%to form a %static 
{\color{blue} of} a {\color{blue}coverage} plan %that visits every point in space 
{\color{blue}and its} {\color{blue}energy-aware} %other to
re-plan{\color{blue}ing} and -schedul{\color{blue}ing } %the plan 
in-flight. %in an energy-aware way. %{\color{blue}, whereas }
{\color{blue} 
The re-planning-scheduling improves a performance metric, which is %quality of the plan and schedule against battery state of charge (SoC), i.e., the 
the weighted average of parameters divided by the remaining battery state of charge (SoC), both in percent. The objective is then high average parameters configuration and battery usage.
%The performance metric the re-planning-scheduling %in the letter 
%improves is %then
%the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
%SoC.% at the end of the flight.
}\vspace*{-2ex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energy Models}  %
\label{sec:energy-model} %
                         %
The solution to the problem requires energy models, predicting the impact of changes to path and computation parameters on the battery. %at future time instants. To this end, 
Sections~\ref{sec:mod-mot}--\hyperref[sec:mod-bat]{C} provide models for the overall and computations energies {\color{blue}and }%as well as 
battery evolution.
